Fluent statistical computing interfaces for biological data analysis

### 2020-10-21 Rmd/01-intro.Rmd
typo corrections

Exploratory data analysis (EDA) is a vital element of the modern 
statistical workflow - it is an analyst’s first pass at 
understanding their data; revealing all it’s messes and 
uncovering hidden insights [@Tukey1977-pn; @Grolemund2017-uc]. 
It is an iterative process involving computation and visualization,
leading to new hypotheses that can be tested and formalised using 
statistical modelling (figure \@ref(fig:wflow-cycle)). As datasets grow in complexity and become
increasingly heterogeneous and multidimensional, 
the use of EDA becomes vital to ensure the integrity and quality of analysis 
outputs. This is certainly true in high-throughput biological 
data science, where constraints on computation time and memory, in addition
to the analyst's time, makes EDA difficult and neglected, which impacts the robustness and reliability of any downstream analysis.

>>>>

Exploratory data analysis (EDA) is a vital element of the modern 
statistical workflow - it is an analyst’s first pass at 
understanding their data; revealing all its messes and 
uncovering hidden insights [@Tukey1977-pn; @Grolemund2017-uc]. 
It is an iterative process involving computation and visualization,
leading to new hypotheses that can be tested and formalised using 
statistical modelling (figure \@ref(fig:wflow-cycle)). As datasets grow in complexity and become
increasingly heterogeneous and multidimensional, 
the use of EDA becomes vital to ensure the integrity and quality of analysis 
outputs. This is certainly true in high-throughput biological 
data science, where constraints on computation time and memory, in addition
to the analyst's time, makes EDA difficult and neglected, which impacts the robustness and reliability of any downstream analysis.

### 2020-10-21 Rmd/02-plyranges.Rmd
typo corrections

Using **plyranges** and the the Bioconductor package **AnnotationHub** [@R-ahub]
we can download and read BigWig files from ChIP-Seq experiments from 
the Human Epigenome Roadmap project [@Roadmap-Epigenomics-Consortium2015-pr]. 
Here we analyse a BigWig file corresponding to H3 lysine 27 trimethylation 
(H3K27Me3) of primary T CD8+ memory cells from peripheral blood, focussing
on coverage islands over chromosome 10.

>>>>

Using **plyranges** and the Bioconductor package **AnnotationHub** [@R-ahub]
we can download and read BigWig files from ChIP-Seq experiments from 
the Human Epigenome Roadmap project [@Roadmap-Epigenomics-Consortium2015-pr]. 
Here we analyse a BigWig file corresponding to H3 lysine 27 trimethylation 
(H3K27Me3) of primary T CD8+ memory cells from peripheral blood, focussing
on coverage islands over chromosome 10.
